Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-10 prop_letter.tex
prop_letter.tex Abstract Updated...

\begin{abstract}~
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision.
\item [{Method}] We model the idea of the finite precision measurement
as finite number of intervals, and replace quantum real-valued probability
measures by interval-valued ones.
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear.
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.

\end{description}
\end{abstract}

@@

In particular, the effect of finite precision on contextuality, and the Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval valued probability measure framework that we introduce.  To proceed, we use a formulation of the Mermin square that uses the
expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}
  \label{sec:Interval-Uncertainty}
We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

>>>>

\begin{abstract}
It is well-known that any quantum measurement can be only performed
in finite precision. However, quantum theory is usually based on infinitely
precise real and complex numbers, and physicists handle this imperfection
by statistical methods without understanding how finite precision
measurement affect the mathematical foundation of quantum theory.
Our purpose here is to examine a quantum model cooperating the idea
of finite precision at very beginning. Within our quantum interval-valued
probability measure (QIVPM) framework, we found a QIVPM become classical
when the projectors all commute, and the expectation value of an observable
can still be computed as expected. Two fundamental quantum theorems,
the Kochen-Specker and Gleason theorem, can be reformulated by QIVPM
given a particular choice of intervals, and we can discuss their validity
within a certain bound. Our research provides a new insight to quantify
the idea of finite precision measurement, and provides a possible
resolution of the Meyer-Mermin debate on the impact of finite precision
on the Kochen-Specker theorem.
\end{abstract}

@@

In particular, the effect of finite precision on contextuality, and the
Kochen-Specker theorem, is shown to have a resolution in terms of the quantum interval-valued probability measure framework that we introduce.  To proceed, we use a formulation of the Mermin square that uses the
expectation value of an observable with respect
to a QIVPM can be defined to be consistent with the constraints on the
expectation value of the same observable expected from continuous
quantum mechanics.  We then examine Gleason's
theorem\nb\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the
Kochen-Specker theorem in the context of QIVPM's, and conclude that
they correspond to the limit of an infinite number of precise
intervals, and the set of cryptodeterministic intervals (the set\nb$\{\imposs,\necess\}$),
respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}
  \label{sec:Interval-Uncertainty}
We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.
